---
title: "cal"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  md_document   
---

```{r, echo=FALSE}
desc <- suppressWarnings(readLines("DESCRIPTION"))
regex <- "(^Version:\\s+)(\\d+\\.\\d+\\.\\d+)"
loc <- grep(regex, desc)
ver <- gsub(regex, "\\2", desc[loc])
#verbadge <- sprintf('<a href="https://img.shields.io/badge/Version-%s-orange.svg"><img src="https://img.shields.io/badge/Version-%s-orange.svg" alt="Version"/></a></p>', ver, ver)
verbadge <- ''
````

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
knit_hooks$set(htmlcap = function(before, options, envir) {
  if(!before) {
    paste('<p class="caption"><b><em>',options$htmlcap,"</em></b></p>",sep="")
    }
    })
knitr::opts_knit$set(self.contained = TRUE, cache = FALSE, fig.align = 'center')
knitr::opts_chunk$set(fig.path = "tools/figure/")
options(scipen=999)
```


[![Build Status](https://travis-ci.org/trinker/cal.svg?branch=master)](https://travis-ci.org/trinker/cal)
[![Coverage Status](https://coveralls.io/repos/trinker/cal/badge.svg?branch=master)](https://coveralls.io/r/trinker/cal?branch=master)
`r verbadge`

**cal** is an R package designed to partially mimic the [Unix `cal`](https://www.tutorialspoint.com/unix_commands/cal.htm) command line tool for generating ascii calendars in the console.

# Installation

To download the development version of **cal**:

Download the [zip ball](https://github.com/trinker/cal/zipball/master) or [tar ball](https://github.com/trinker/cal/tarball/master), decompress and run `R CMD INSTALL` on it, or use the **pacman** package to install the development version:

```r
if (!require("pacman")) install.packages("pacman")
pacman::p_load_current_gh("trinker/cal")
```


# Examples:

```{r}
cal()
cal("2017")
cal("03")
cal("Jan")
cal("december")
cal("2:5")
cal("-r 4")
cal("-r 3")
cal("-r -3")
cal("-r -3:4")
cal("03 2015")
cal("Jan 2015")
cal("January 2015")
```
# Contact

You are welcome to:    
- submit suggestions and bug-reports at: <https://github.com/trinker/cal/issues>    
- send a pull request on: <https://github.com/trinker/cal>    
- compose a friendly e-mail to: <tyler.rinker@gmail.com>    
